|

### 2022-12-29 paper.Rmd
autogit

WIDTH=1600
HEIGHT=1200
THEME="neutral"
BACKGROUND="transparent"

@@

````

@@

![DAE-GP - Algorithm](./img/flowcharts/dae-gp.png)

@@

![DAE-GP - Algorithm](./img/flowcharts/pt-dae-gp.png)

@@

![Airfoil - First Generation Median Training Error for variable number of hidden Neurons](./img/airfoil_firstGen/airfoil_firstGen_median_training_error_by_neurons.png)

![Airfoil - First Generation final Training Error for variable number of hidden Neurons](./img/airfoil_firstGen/airfoil_firstGen_boxplot_training_error_by_neurons.png)

@@

![Airfoil - First Generation Median Training Error for variable number of hidden Layers](./img/airfoil_firstGen/airfoil_firstGen_mean_training_error_by_layers.png)

![Airfoil - First Generation final Training Error for variable number of hidden Layers](./img/airfoil_firstGen/airfoil_firstGen_boxplot_training_error_by_layer.png)

@@

![Airfoil - Best Fitness over 30 Generations](./img/airfoil_FullRun_30gens/mean_median_fitness_byGens.png)

@@

![Airfoil - Fitness Distribution Boxplot](./img/airfoil_FullRun_30gens/final_fit_boxplot.png)

![Airfoil - Average Population Diversity](./img/airfoil_FullRun_30gens/mean_popDiversity_byGens.png)
Since @dae-gp_2022_symreg shows, that DAE-GP finds higher quality that are also smaller in size than those found by average GP for a given number of 10.000 fitness evaluations, I also studied the differences in average solution size between pre-trained and regular DAE-GP.

![Airfoil - Average Solution Size](./img/airfoil_FullRun_30gens/mean_Size_byGens.png)

>>>>

WIDTH=3200
HEIGHT=2400
THEME="neutral"
BACKGROUND="white"

@@

@@

![Flowchart - Regular DAE-GP](./img/flowcharts/dae-gp.png){height=800px width=200px}

@@

![Flowchart - Pre-Trained DAE-GP](./img/flowcharts/pt-dae-gp.png){height=800px width=200px}

@@

![First Generation Median Training Error for variable number of hidden Neurons - Airfoil](./img/airfoil_firstGen/airfoil_firstGen_median_training_error_by_neurons.png)

![First Generation final Training Error for variable number of hidden Neurons - Airfoil](./img/airfoil_firstGen/airfoil_firstGen_boxplot_training_error_by_neurons.png)

@@

![First Generation Median Training Error for variable number of hidden Layers - Airfoil](./img/airfoil_firstGen/airfoil_firstGen_mean_training_error_by_layers.png)

![First Generation final Training Error for variable number of hidden Layers - Airfoil](./img/airfoil_firstGen/airfoil_firstGen_boxplot_training_error_by_layer.png)

@@

![Best Fitness over 30 Generations - Airfoil](./img/airfoil_FullRun_30gens/mean_median_fitness_byGens.png)

@@

![Best Fitness Distribution after 30 Generations - Airfoil](./img/airfoil_FullRun_30gens/final_fit_boxplot.png)
lalal

![Population Diversity over 30 Generations - Airfoil](./img/airfoil_FullRun_30gens/mean_popDiversity_byGens.png)
Since @dae-gp_2022_symreg shows, that DAE-GP finds higher quality that are also smaller in size than those found by average GP for a given number of 10.000 fitness evaluations, I also studied the differences in average solution size between pre-trained and regular DAE-GP.

![Average Solution Size over 30 Generations - Airfoil](./img/airfoil_FullRun_30gens/mean_Size_byGens.png)
